Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-23 doc/manuscript/ESSDmanuscript.Rmd
split record_of_changes table across pages
previously ran off the page.

This change moved caption to center.

library(knitr)
library(kableExtra)
knitr::kable(record_of_changes, format = "latex",
             longtable = FALSE,
             caption = "\\textbf{Table of changes to ForC fields.}") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)
```

>>>>

library(knitr)
library(kableExtra)
knitr::kable(record_of_changes, format = "latex",
             longtable = TRUE,
             caption = "\\textbf{Table of changes to ForC fields.}") %>%
  kableExtra::kable_styling(full_width = TRUE, latex_options = c("repeat_header")) %>%
  row_spec(0, bold = TRUE)
```

### 2021-06-23 doc/manuscript/ESSDmanuscript.tex
split record_of_changes table across pages
previously ran off the page.

This change moved caption to center.

\caption{\label{tab:table_ForCchanges}\textbf{Table of changes to ForC fields.}}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{Table} & \textbf{Column} & \textbf{Description} & \textbf{Changes} & \textbf{Motivation}\\
\hline
Sites & coordinates.precision & Precision of geographic coordinates, as reported by source or estimated from maps. & field added & allow identification of records with poor coordinate precision\\
\hline
Measurements & data.location.within.source & Location of data within the source listed in citation.ID. & field added & facilitate review, ensure traceability\\
\hline
 & sd, se, lower95\%CI, upper 95\%CI & Standard deviation, standard error, and lower and upper 95 percent confidence intvervals, respectively. & replaces `stat` and `stat.name` & cleaner format; ability to handle assymetrical 95 percent confidence intervals\\
\hline
 & mean.in.original.units, original.units & mean value and units presented in original publication & fields added & provide IPCC with original units, reduce errors/improve reproducibility\\
\hline
 & C.conversion.factor & Assumed/ measured C content of organic matter used to convert organic matter to C. & field added & track units conversion, allow back-calculation of OM if conversion factor deemed inappropriate\\
\hline
PFT & description & Definition of the pftcode at the community level. Differs from individual level in that properly describes mixed plant functional types. & field added & \\
\hline
 & description.individual & Definition of the pftcode at the individual plant level. & field name change (previously `description`) & \\
\hline
Citations & citation.citation & Full citation. Most of these records are automatically generated in R based upon DOI lookup. & field added & field required by IPCC\\
\hline
 & citation.language & Language of original publication, automatically generated based on the title and abstract, with some manual entries and corrections. & field added & field required by IPCC\\
\hline
 & citation.url & URL of original publication, generally retrieved automatically via URL lookup. & field added & field required by IPCC\\
\hline
 & citation.abstract & Abstract, generally retrieved automatically via DOI lookup. & field added & field required by IPCC\\
\hline
 & pdf.in.repository & Indicates whether pdf of original study has been retrieved and saved in ForC's reference repository & field added & housekeeping\\
\hline
\end{tabu}
\end{table}

>>>>

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:table_ForCchanges}\textbf{Table of changes to ForC fields.}}\\
\hline
\textbf{Table} & \textbf{Column} & \textbf{Description} & \textbf{Changes} & \textbf{Motivation}\\
\hline
\endfirsthead
\caption[]{\textbf{Table of changes to ForC fields.} \textit{(continued)}}\\
\hline
\textbf{Table} & \textbf{Column} & \textbf{Description} & \textbf{Changes} & \textbf{Motivation}\\
\hline
\endhead
Sites & coordinates.precision & Precision of geographic coordinates, as reported by source or estimated from maps. & field added & allow identification of records with poor coordinate precision\\
\hline
Measurements & data.location.within.source & Location of data within the source listed in citation.ID. & field added & facilitate review, ensure traceability\\
\hline
 & sd, se, lower95\%CI, upper 95\%CI & Standard deviation, standard error, and lower and upper 95 percent confidence intvervals, respectively. & replaces `stat` and `stat.name` & cleaner format; ability to handle assymetrical 95 percent confidence intervals\\
\hline
 & mean.in.original.units, original.units & mean value and units presented in original publication & fields added & provide IPCC with original units, reduce errors/improve reproducibility\\
\hline
 & C.conversion.factor & Assumed/ measured C content of organic matter used to convert organic matter to C. & field added & track units conversion, allow back-calculation of OM if conversion factor deemed inappropriate\\
\hline
PFT & description & Definition of the pftcode at the community level. Differs from individual level in that properly describes mixed plant functional types. & field added & \\
\hline
 & description.individual & Definition of the pftcode at the individual plant level. & field name change (previously `description`) & \\
\hline
Citations & citation.citation & Full citation. Most of these records are automatically generated in R based upon DOI lookup. & field added & field required by IPCC\\
\hline
 & citation.language & Language of original publication, automatically generated based on the title and abstract, with some manual entries and corrections. & field added & field required by IPCC\\
\hline
 & citation.url & URL of original publication, generally retrieved automatically via URL lookup. & field added & field required by IPCC\\
\hline
 & citation.abstract & Abstract, generally retrieved automatically via DOI lookup. & field added & field required by IPCC\\
\hline
 & pdf.in.repository & Indicates whether pdf of original study has been retrieved and saved in ForC's reference repository & field added & housekeeping\\
\hline
\end{longtabu}
